Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2018-01-05 ms.tex
adding summary

WASP-103b is an archetype of the class of ultra-hot Jupiters (with orbital periods of about one day and dayside temperatures typically $>2000\,\mathrm{K}$). Observations of the thermal emission spectra of these objects have been puzzling. In the near-infrared, where water is the dominant absorber, some spectra show water absorption features, some show emission features, and some are consistent with blackbody models \citep{madhusudhan11, crossfield12, stevenson14b, haynes15, evans16, beatty17a, beatty17b, sheppard17, arcangeli18, mansfield18}.  A variety of explanations were proposed for these results, including low metallicity or high carbon-to-oxygen compositions, dayside clouds, and isothermal or inverted temperature profiles caused by TiO/VO absorption in the upper atmosphere. Recently, \cite{arcangeli18} showed that water dissociation on the hot dayside plays an important role in the atmospheres of these ultra-hot planets and may be responsible for some of the blackbody-like near-IR spectra. In this work, we put these results in context investigate the global thermal structure of WASP-103b over a range of temperatures. FIXME

The structure of the paper is the following: in \S\,\ref{sec:observations} we describe the observations and data reduction. \S\,\ref{sec:fits} details the models fit to the phase curves. \S\,\ref{sec:results} we discuss results, including the phase-resolved spectra, a comparison of thermal phase variation models, and FIXME. In \S\,\ref{sec:gcm} and \ref{sec:comparison}, we compare the observations to GCM predictions and spectra from similar temperature stars and directly imaged companions. \S\,\ref{sec:discussion} concludes.

@@

The main spectral feature over the wavelength range we consider is water. To quantitatively compare the water feature amplitude for different objects, we define an amplitude $A = (R_\mathrm{1.3} - R_\mathrm{1.5})/F_\mathrm{1.3}$, where $F_\mathrm{X}$ is the average flux in a wavelength bin $0.1\,\mu$m wide centered on a wavelength $X$, and $R_\mathrm{X}$ is the bin-averaged residual from the best fit blackbody. These intervals were chosen such that all of the data have complete spectral coverage over the bin.

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/spectra_comparison.pdf}
\caption{Spectra for WASP-103b (left column) compared to brown dwarfs (middle) and directly imaged companions (right). The WASP-103b spectra are from the nightside (phase 0.1, top row), quadrature (phase 0.25, middle) and the dayside (phase 0.5, bottom). Each row shows spectra from objects of comparable temperature. The dotted gray line corresponds to the best fit blackbody. Effective temperatures are listed in the upper right corners.}
\label{fig:planetstarcomparison}
\end{figure*}

@@

\section{Discussion and Conclusions}
\label{sec:discussion}
One-dimensional retrieval is probably wrong, since we showed the dayside may have a large temperature gradient -> should work on this in the future.

There are many factors contributing to the blackbody spectra --
weak water xsec contrast, isothermal pt, H-, and dissociated water, gravity (cite T. Beatty)

Cite Feng et al. 2016.

H- is important.

How does composition compare to other HJs (esp W43b)
The spectrum is similar to observations of several other ultra-hot Jupiters \citep[][]{arcangeli18, mansfield18}, but qualitatively different from slightly cooler planets, which show water absorption features in the near-infared \citep[e.g.][]{kreidberg14b, line16}.

eclipse mapping to break degeneracy in models

We rule out the low metallicity and or high C/O models

confirm prediction that TiO is present in the hottest planets

what do the hot spot offsets and amplitudes mean?

>>>>

WASP-103b is an archetype of the class of ultra-hot Jupiters (with orbital periods of about one day and dayside temperatures typically $>2000\,\mathrm{K}$). Observations of the thermal emission spectra of these objects have been puzzling. In the near-infrared, where water is the dominant absorber, some spectra show water absorption features, some show emission features, and some are consistent with blackbody models \citep{madhusudhan11, crossfield12, stevenson14b, haynes15, evans16, beatty17a, beatty17b, sheppard17, arcangeli18, mansfield18}.  A variety of explanations have been proposed for these results, including low metallicity or high carbon-to-oxygen compositions, dayside clouds, and isothermal or inverted temperature profiles caused by TiO/VO absorption in the upper atmosphere. Recently, \cite{arcangeli18} showed that water dissociation on the hot dayside plays an important role in the atmospheres of these ultra-hot planets and may be responsible for some of the blackbody-like near-IR spectra. In this work, we put these results in context investigate the global thermal structure of WASP-103b over a range of temperatures. FIXME

The structure of the paper is the following: in \S\,\ref{sec:observations} we describe the observations and data reduction. \S\,\ref{sec:fits} details the models fit to the phase curves. \S\,\ref{sec:results} we discuss results, including the phase-resolved spectra, a comparison of thermal phase variation models, and FIXME. In \S\,\ref{sec:gcm} and \ref{sec:comparison}, we compare the observations to GCM predictions and spectra from similar temperature stars and directly imaged companions. \S\,\ref{sec:summary} concludes.

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/spectra_comparison.pdf}
\caption{Flux-calibrated spectra for WASP-103b (left column) compared to brown dwarfs (middle) and directly imaged companions (right), assuming a distance of 10 pc. The WASP-103b spectra are from the nightside (phase 0.1, top row), quadrature (phase 0.25, middle) and the dayside (phase 0.5, bottom). Each row shows spectra from objects of comparable temperature. The dotted gray line corresponds to the best fit blackbody. Effective temperatures are listed in the upper right corners. The wavelength bins used to calculate the water feature amplitude $A_1$ are shaded in gray.}
\label{fig:planetstarcomparison}
\end{figure*}

The main spectral feature over the wavelength range we consider is water. To quantitatively compare the water feature amplitude for different objects, we define an amplitude $A = (F_{\lambda_1, \lambda_2} - F_{\lambda_3, \lambda_4})/F_{\lambda_1,\lambda_2}$, where $F_{\lambda_x, \lambda_y}$ is the weighted mean flux in a wavelength bin $x - y$. We calculated the water feature amplitude for two choices of wavelength bins. For the first, $A_1$, we considered data in and out of the water band, with $\lambda_{1,2,3,4} = 1.15, 1.3, 1.35, 1.5\,\mu$m. The ground-based direct imaging data doesn't span this entire wavelength, so we also define an amplitude $A_2$ with $\lambda_{1,2,3,4} = 1.2, 1.35, 1.5, 1.65\,\mu$m. The estimated amplitudes and uncertainties are listed in Table\,\ref{table:sources}.

For WASP-103b, $A_1$ is consistent with zero at all three orbital phases. The brown dwarfs have similar

@@

\section{Summary}
\label{sec:summary}
We observed thermal phase curves of the hot Jupiter WASP-103b measured with \HST/WFC3 time series spectroscopy ($1.15 - 1.65\,\mu$m) and \Spitzer/IRAC broadband photometry ($3.6$ and $4.6\,mu$m bands).

\begin{itemize}
	\item{We fit the climate using the \texttt{spiderman} package \citep{louden17}}
	\item{The phase curves have large amplitude ($0.8 -0.9\times$ secondary eclipse depth)}
	\item{The phase-resolved spectra are consistent with a blackbody model, but there is an emission feature at \Spitzer\ wavelengths. Why is it isothermal? cite Beatty} 
	\item{We characterized the composition with a 1D grid-based retrieval. The atmospheric metallicity is super-solar () and > 1 at $3\,\sigma$ confidence. larger than  } 
	\item{We compared the phase curves to 3D GCM predictions}
	\item{We compared the spectra to brown dwarfs and directly imaged companions of similar temperature}
\end{itemize}

%Cite Feng et al. 2016.

%H- is important.

%How does composition compare to other HJs (esp W43b)
%The spectrum is similar to observations of several other ultra-hot Jupiters \citep[][]{arcangeli18, mansfield18}, but qualitatively different from slightly cooler planets, which show water absorption features in the near-infared \citep[e.g.][]{kreidberg14b, line16}.

%eclipse mapping to break degeneracy in models

%We rule out the low metallicity and or high C/O models

%confirm prediction that TiO is present in the hottest planets

%what do the hot spot offsets and amplitudes mean?
